\section{PS11, Ex. 1 (A): Effect of the GED education as a signal}

\begin{frame}{PS11, Ex. 1 (A): Effect of the GED education as a signal}
    Does signaling work? Read the article by Tyler, Murnane and Willett and think about
    their results. What is their hypothesis for why they do not find an effect for minority groups? Come up with an example of an education program that has mostly signaling value in your country.\\\medskip
    \textit{(This is a reflection question, no answer will be provided).}
    \vfill\null
\end{frame}



\section{PS11, Ex. 2 (A): Asymmetric information (PBE)}

\begin{frame}{PS11, Ex. 2 (A): Asymmetric information (PBE)}
    Exercise 4.11 in Gibbons (p. 250). Difficult. A buyer and a seller have valuations $v_b$ and $v_s$. It is common knowledge that there are gains from trade (i.e., that $v_b > v_s$), but the size of the gains is private information, as follows: the seller’s valuation is uniformly distributed on [0,1]; the buyer’s valuation $v_b = kv_s$, where $k > 1$ is common knowledge; the seller knows $v_s$ (and hence $v_b$) but the buyer does not know $v_b$ (and hence $v_s$). Suppose the buyer makes a single offer, $p$, which the seller either accepts or rejects. What is the perfect Bayesian equilibrium when $k < 2$? When $k > 2$? (See Samuelson 1984.)
    \vfill\null
\end{frame}

\begin{frame}{PS11, Ex. 2 (A): Asymmetric information (PBE)}
    Exercise 4.11 in Gibbons (p. 250). Difficult. A buyer and a seller have valuations $v_b$ and $v_s$. It is common knowledge that there are gains from trade (i.e., that $v_b > v_s$), but the size of the gains is private information, as follows: the seller’s valuation is uniformly distributed on [0,1]; the buyer’s valuation $v_b = kv_s$, where $k > 1$ is common knowledge; the seller knows $v_s$ (and hence $v_b$) but the buyer does not know $v_b$ (and hence $v_s$). Suppose the buyer makes a single offer, $p$, which the seller either accepts or rejects. What is the perfect Bayesian equilibrium when $k < 2$? When $k > 2$? (See Samuelson 1984.) \vspace{-8pt}
    \begin{multicols}{2}
      \vfill\null\columnbreak
      \vfill\null
    \end{multicols}
\end{frame}
