\section{PS8, Ex. 5: The dating game (Bayesian Nash Equilibria)}

\begin{frame}{PS8, Ex. 5: The dating game (Bayesian Nash Equilibria)}
    Consider the ‘dating game’. In this game, player 1 wants to meet with player 2, even if player 2 is of type $t_2$, who does not want to meet with player 1. Player 2’s types have equal probability.\\\medskip
    Now suppose we construct an alternative version of the game, where player 1 has self respect, and only wants to meet up with player 2 if player 2 also wants to meet up (i.e. if player 2 is of type $t_1$). Otherwise, player 1 prefers to $miscoordinate$ (i.e. not to meet up) as well. Player 1 still has the same preference for going to football versus the opera.
    \begin{itemize}
      \item[(a)] Write up this new game. Use the same payoffs as before (0,1, and 2) such that the payoff matrix when player 2’s type is $t_1$ is the same as in the slides (Lecture 7, slides 22-26).
      \item[(b)] Find the set of (pure strategy) Bayesian Nash Equilibria of this game.
    \end{itemize}
    \textit{[Hints on next slide.]}
    \vfill\null
\end{frame}
\begin{frame}{PS8, Ex. 5: The dating game (Bayesian Nash Equilibria)}
    Consider the ‘dating game’. In this game, player 1 wants to meet with player 2, even if player 2 is of type $t_2$, who does not want to meet with player 1. Player 2’s types have equal probability.\\\medskip
    Now suppose we construct an alternative version of the game, where player 1 has self respect, and only wants to meet up with player 2 if player 2 also wants to meet up (i.e. if player 2 is of type $t_1$). Otherwise, player 1 prefers to $miscoordinate$ (i.e. not to meet up) as well. Player 1 still has the same preference for going to football versus the opera.
    \begin{itemize}
      \item[(a)] Write up this new game. Use the same payoffs as before (0,1, and 2) such that the payoff matrix when player 2’s type is $t_1$ is the same as in the slides (Lecture 7, slides 22-26).
    \end{itemize}
    \textbf{\textit{Hint:}} Write up the Bayesian game (players, type spaces, beliefs, action spaces, strategy spaces, and the type-dependent payoff matrices.)
    \begin{itemize}
      \item[(b)] Find the set of (pure strategy) Bayesian Nash Equilibria of this game.
    \end{itemize}
    \textbf{\textit{Hints:}}
    \begin{enumerate}
      \item Check for equilibria where player 1 plays $Football$ and $Opera$ respectively.
      \item In equilibrium, a strategy should maximize expected payoff given the strategy of the other player and the probability of each type.
    \end{enumerate}
    \vfill\null
\end{frame}

\begin{frame}{PS8, Ex. 5.a: The dating game (Bayesian Nash Equilibria)}
    \begin{itemize}
      \item[(a)] Write up this new game. Use the same payoffs as before (0,1, and 2) such that the payoff matrix when player 2’s type is $t_1$ is the same as in the slides (Lecture 7, slides 22-26).
    \end{itemize}
    \vspace{-4pt}
    \begin{enumerate}
      \item Players: P1, P2.
      \item Type spaces: $T_1=\{t\},\ T_2=\{t_1,t_2\}$
      \item Beliefs: $\mathbb{P}_1(T_2=t_1)=\mathbb{P}_1(T_2=t_2)=\frac{1}{2},\ \mathbb{P}_2(T_1=t)=1$
      \item Action space: $A_i=\{Football,Opera\},\text{ for }i\in1,2$
      \item Strategy spaces: $S_1=\{F,O\},\ S_2=\{FF,FO,OF,OO\}$
      \item Type-dependent payoff matrices:
    \end{enumerate}
    \vspace{-8pt}
    \begin{table}
      \begin{tabular}{l|c|c|}
        \multicolumn{1}{c}{} & \multicolumn{2}{c}{Type $t_1\ (p=\frac{1}{2})$} \\
        \multicolumn{1}{c}{} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{O} \\\cline{2-3}
        F & 2, 1 & 0, 0 \\\cline{2-3}
        O & 0, 0 & 1, 2 \\\cline{2-3}
      \end{tabular}\quad
      \begin{tabular}{l|c|c|}
        \multicolumn{1}{c}{} & \multicolumn{2}{c}{Type $t_2\ (p=\frac{1}{2})$} \\
        \multicolumn{1}{c}{} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{O} \\\cline{2-3}
        F & 0, 0 & 2, 2 \\\cline{2-3}
        O & 1, 1 & 0, 0 \\\cline{2-3}
      \end{tabular}
    \end{table}
    \vfill\null
\end{frame}

\begin{frame}{PS8, Ex. 5.b: The dating game (Bayesian Nash Equilibria)}
    \begin{table}
      \begin{tabular}{l|c|c|}
        \multicolumn{1}{c}{} & \multicolumn{2}{c}{Type $t_1\ (p=\frac{1}{2})$} \\
        \multicolumn{1}{c}{} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{O} \\\cline{2-3}
        F & 2, 1 & 0, 0 \\\cline{2-3}
        O & 0, 0 & 1, 2 \\\cline{2-3}
      \end{tabular}\quad
      \begin{tabular}{l|c|c|}
        \multicolumn{1}{c}{} & \multicolumn{2}{c}{Type $t_2\ (p=\frac{1}{2})$} \\
        \multicolumn{1}{c}{} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{O} \\\cline{2-3}
        F & 0, 0 & 2, 2 \\\cline{2-3}
        O & 1, 1 & 0, 0 \\\cline{2-3}
      \end{tabular}
    \end{table}
    \begin{itemize}
      \item[(b)] Find the set of (pure strategy) Bayesian Nash Equilibria of this game.
    \end{itemize}
  \begin{multicols}{2}
    \vfill\null\columnbreak
    \vfill\null
  \end{multicols}
\end{frame}



\section{PS8, Ex. 6: }

\begin{frame}{PS8, Ex. 6: }
  \begin{multicols}{2}
    Difficult. Consider the public goods game from lecture 7. Suppose now instead that there is two-sided incomplete information. In particular, the cost of writing the reference is uniformly distributed between 0 and 2:
    \begin{align*}
      c_i\sim u(0,2)\text{ for }i=1,2
    \end{align*}
    In this setting, we can show that the players optimally follow a ‘cutoff’ strategy. Thus, the equilibrium strategies take the form
    \begin{align*}
      s_1^*(c_1)&=\left\{\begin{array}{rcl}
        Write & \text{if} & c_1\leq c_1^*\\
        Don't & \text{if} & c_1>c_1^*
        \end{array}\right.\\
      s_2^*(c_2)&=\left\{\begin{array}{rcl}
        Write & \text{if} & c_2\leq c_2^*\\
        Don't & \text{if} & c_2>c_2^*
        \end{array}\right.
    \end{align*}
    \vfill\null\columnbreak
    \begin{itemize}
      \item[(a)] Let $z_{-i}^* = \mathbb{P}(s_{-i}^*=Write)$, i.e. the probability that the other player plays 'Write' in equilibrium. Argue that
      \vspace{-18pt}
      \begin{align}
        1-c_i^*=z_{-i}^*\label{7a}
      \end{align}
      \textit{Hint:} Calculate $i$'s expected payoff from writing the reference and from not writing the reference, conditional on $z_{-i}^*$.
      \item[(b)] A standard result on uniform distributions gives the following: if $x\sim u(0, 2)$, then $\mathbb{P}(x<a)=\frac{a}{2}$. Use this to find $z_i^*$. $Hint:$ Use the equilibrium strategy and your knowledge of the distribution of $c_{-i}$.
      \item[(c)] Use the result from (b) together with eq. \eqref{7a} to find $(c_1^* , c_2^*)$.
      \item[(d)] What’s the probability of under- investment (i.e. that nobody writes the reference)? What’s the prob. of overinvestment (i.e. both write)?
    \end{itemize}
    \vfill\null
  \end{multicols}
\end{frame}

\begin{frame}{PS8, Ex. 6.a: }
  \begin{multicols}{2}
    \vfill\null\columnbreak
    \vfill\null
  \end{multicols}
\end{frame}
